О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-06 pps-linear-bound/pps-linear-lower-bound.tex
Move the last conjecture to the appropriate section

\begin{conjecture}
	\label{hyp:prime_planar}
	For every $m \geq 2$, $n \geq m+1$, $d \geq 1$ there exists an \textbf{prime}
	integral point set $M\in\mathfrak{M}(m,n)$ which
	contains points $M_1$ and $M_2$ such that distance between $M_1$ and $M_2$ is exactly $d$.
\end{conjecture}

For $m \geq 3$, Conjecture~\ref{hyp:prime_planar} can be easily proved:
indeed, we can just take a facher integral point set according to Construction~\ref{con:planar_set_with_minimeter_1}
with sufficiently large height and then apply the ``blowing up'' procedure described in~\cite[Theorem 1.3]{kurz2008bounds},
replacing the out-of-line point with an $(m-2)$-dimensional simplex of proper side length.
That simplex will consist of $m-1$ points;
we can throw out up to all points $M_J$, except the two points with distance 1.
So, the set consists of $m+1$ or more points and has distance 1 occuring in it.
As distance 1 occurs in the obtained set, it is prime.

So, Conjecture~\ref{hyp:prime_planar} needs proof only for $m=2$.
For $m>2$, a bit more strong result can also be claimed.

\begin{theorem}
	For arbitrary integers $m > 2$, $n \geq m+1$, $d \geq 1$
	there exists a prime set $M\in\mathfrak{M}(m,n)$,
	such that for some $M_1, M_2\in M$ equality $|M_1 M_2| = d$ holds,
	the distance $d$ is minimal and occurs in $M$ only once.
\end{theorem}

@@

\begin{problem}
	For $M\in\mathfrak{M}(m,n)$, how many times can the distance 1 occur in $M$?
\end{problem}
The answer for $m=2$ is given by Theorem~\ref{thm:minimeter_1_planar}.
For greater $m$, we will be brave enough to put forward
\begin{conjecture}
	Consider $M\in\mathfrak{M}(m,n)$, $M_1,M_2\in M$, $|M_1 M_2| =1$.
	Then either $n = m+1$ or $M$ is a ``blowup'' of a facher set and distance 1 occurs in $m$
	not more than $1+\frac{m^2 - m}{2}$ times.
\end{conjecture}
Such as estimate is based on the quantity of edges in $(m-1)$-dimensional simplex.

>>>>

\begin{theorem}
	\label{thm:prime_with_desired_distance}
	For every $m \geq 3$, $n \geq m+1$, $d \geq 1$ there exists an \textbf{prime}
	integral point set $M\in\mathfrak{M}(m,n)$ which
	contains points $M_1$ and $M_2$ such that distance between $M_1$ and $M_2$ is exactly $d$.
\end{theorem}

\begin{proof}
	Take a facher integral point set according to Construction~\ref{con:planar_set_with_minimeter_1}
	with sufficiently large height and then apply the ``blowing up'' procedure described in~\cite[Theorem 1.3]{kurz2008bounds},
	replacing the out-of-line point with an $(m-2)$-dimensional simplex of proper side length.
	That simplex will consist of $m-1$ points;
	we can throw out up to all points $M_J$, except the two points with distance 1.
	So, the set consists of $m+1$ or more points and has distance 1 occuring in it.
	As distance 1 occurs in the obtained set, it is prime.
\end{proof}

A bit more strong result can also be claimed.

\begin{theorem}
	\label{thm:prime_with_unique_desired_distance}
	For arbitrary integers $m > 2$, $n \geq m+1$, $d \geq 1$
	there exists a prime set $M\in\mathfrak{M}(m,n)$,
	such that for some $M_1, M_2\in M$ equality $|M_1 M_2| = d$ holds,
	the distance $d$ is minimal and occurs in $M$ only once.
\end{theorem}

@@

\begin{problem}
	For $M\in\mathfrak{M}(m,n)$, how many times can the distance 1 occur in $M$?
\end{problem}
The answer for $m=2$ is given by Theorem~\ref{thm:minimeter_1_planar}.
For greater $m$, we will be brave enough to put forward
\begin{conjecture}
	Consider $M\in\mathfrak{M}(m,n)$, $M_1,M_2\in M$, $|M_1 M_2| =1$.
	Then either $n = m+1$ or $M$ is a ``blowup'' of a facher set and distance 1 occurs in $m$
	not more than $1+\frac{m^2 - m}{2}$ times.
\end{conjecture}
Such as estimate is based on the quantity of edges in $(m-2)$-dimensional simplex.

We want to end the list of conjectures with the one which looks the easiest to deal with.

\begin{conjecture}
	\label{hyp:prime_planar}
	For every $n \geq 3$, $d \geq 1$ there exists an \textbf{prime}
	set $M\in\mathfrak{M}(2,n)$ which
	contains points $M_1$ and $M_2$ such that distance between $M_1$ and $M_2$ is exactly $d$.
\end{conjecture}
This conjecture gives the same claim with Theorem~\ref{thm:prime_with_desired_distance}, but for $m=2$.
Obviously, Theorem~\ref{thm:prime_with_unique_desired_distance} can be generalized (for $m=2$) into a similar conjecture.
